Sky Tomography for 3D Aerosol Distribution Recovery

### 2013-07-22 article.tex
bf -> bm due to font problems (note that it is good only for math symbols and not for text)

Consider \cref{fig:groundgrid}.  Ground-based wide-angle sky-cameras
capture the sky lightfield from below. Per viewpoint, the view azimuth
and elevation angles (relative to the zenith and north) are
encapsulated in the vector ${\bf{\Theta}}$.  A raw image is $i_{\bf
  x}({\bf{\Theta}})$: a camera's location ${\bf x}$ is fixed, while
any pixel in a frame represents an angle ${\bf{\Theta}}$.  The
measured radiance in all locations ${\bf x}$ and angles
${\bf{\Theta}}$ is the {\em lightfield} $I({\bf
  x},{\bf{\Theta}})$. Individual images are slices of the lightfield.

@@

The number of voxels is $N_{\rm voxels}$. All their associated
variables are concatenated into columns stack vectors, each $N_{\rm
  voxels}$ long. Aerosol densities and cross sections in all voxels
are stored in the respective vectors ${\bf n}$ and
$\vect{\sigma}$. Define a $N_{\rm voxels}\times N_{\rm voxels}$ sparse
matrix ${\bf D}^{\mathrm{Sun \rightarrow voxel}}$, whose element
$(k,q)$ is
\begin{equation}
  D^{\mathrm{Sun \rightarrow voxel}}(k,q) =
  \left\{
    \begin{array}{ll}
      l_{\rm SR}(q) & \mbox{ if $q \in[{\rm SR},k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dsv}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
\cref{eq:lSRaeros,eq:Dsv} lead to a vector of SR optical depths due to
aerosols (See \cref{fig:projection})a:
\begin{equation}
  \vect{\tau}_{\rm SR}^{\rm aerosol}=
  {\bf D}^{\mathrm{Sun \rightarrow voxel}}
  (\vect{\sigma} \odot {\bf n})
  \label{eq:tauSRvec1}
\end{equation}
where the operator $\odot$ denotes the Hadamard (element-wise)
product. Similarly, \cref{eq:lSRair} leads to a vector of SR optical
depths due to air, $\vect{\tau}_{\rm SR}^{\rm air}$.

Analogously, for camera $c$, denote by $[{\rm LOS}_c,k]$ a LOS bounded
between the camera and the center of voxel $k$. The LOS zenith angle
is $\Phi^{\rm LOS}_c$.  This LOS intersects voxel $q$. The geometric
length of this intersection line segment is $l_{\rm LOS_c}(q)$which
depends on $\Delta z$, $\Phi^{{\rm LOS}_c}$ and $q$.  Analogously to
\cref{eq:lSRaa,eq:lSRair,eq:lSRaeros}, the optical depth along a LOS
to $k$ is
\begin{equation}
  \tau_{{\rm LOS}_c}(k)=
  \tau_{{\rm LOS}_c}^{\rm air}(k) +  \tau_{{\rm LOS}_c}^{\rm aerosol}(k)
  \;\;,
  \label{eq:lLOSaerot}
\end{equation}
where
\begin{equation}
  \tau_{{\rm LOS}_c}^{\rm air}(k)=
  \sum_{q \in[{\rm LOS}_c,k]}
  \beta^{\rm air}(q)  l_{\rm LOS_c}(q)
  \label{eq:lLOSair}
\end{equation}
and
\begin{align}
  \label{eq:lLOSaeros}
  \tau_{{\rm LOS}_c}^{\rm aerosol}(k) = \sum_{q \in[{\rm LOS}_c,k]}
  \sigma^{\rm aerosol}(q) n^{\rm aerosol}(q) l_{\rm LOS_c}(q).
\end{align}
\cref{eq:lLOSaeros} leads to a vector of LOS optical depths due to
aerosols:
\begin{equation}
  \vect{\tau}_{{\rm LOS}_c}^{\rm aerosol}=
  {\bf D}^{\mathrm{voxel \rightarrow cam}}_c
  (\vect{\sigma} \odot {\bf n})
  \label{eq:tauLOSvec1}
\end{equation}
Here ${\bf D}^{\mathrm{voxel \rightarrow cam}}_c$ is a $N_{\rm
  voxels}\times N_{\rm voxels}$ sparse matrix whose element $(k,q)$ is
\begin{equation}
  D^{\mathrm{voxel \rightarrow cam}}_c(k,q) =
  \left\{
    \begin{array}{ll}
      l_{\rm LOS_c}(q) & \mbox{ if $q \in[{\rm LOS}_c,k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dvc}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
Similarly, \cref{eq:lSRair} leads to a vector of LOS optical depths
due to air, $\vect{\tau}_{{\rm LOS}_c}^{\rm air}$.

The fixed sparse matrices ${\bf D}^{\mathrm{Sun \rightarrow voxel}}$
and ${\bf D}^{\mathrm{voxel \rightarrow cam}}_c$ are compounded to a
single matrix
\begin{equation}
  {\bf D}_c=
  {\bf D}^{\mathrm{Sun \rightarrow voxel}}+
  {\bf D}^{\mathrm{voxel \rightarrow cam}}_c
  \;\;.
  \label{eq:Dtotal}
\end{equation}
Similarly, the molecular optical depths along all trajectories between
the sun, each voxel and camera $c$ are compounded to a vector
\begin{equation}
  \vect{\tau}_c^{\rm air}=
  \vect{\tau}_{\rm SR}^{\rm air}+
  \vect{\tau}_{{\rm LOS}_c}^{\rm air}
  \;\;.
  \label{eq:tauairtotal}
\end{equation}
Using \cref{eq:rayleighbeta} for $\beta^{\rm air}$ in all voxels, the
vector $\vect{\tau}_c^{\rm air}$ is fixed. Thus $\vect{\tau}_c^{\rm
  air}$ can be calculated once, per sun zenith angle.

Using
\cref{eq:lSRaa,eq:tauSRvec1,eq:lLOSair,eq:tauLOSvec1,eq:Dtotal,eq:tauairtotal},
the total optical depths corresponding to LOSs (of camera $c$) and SRs
that cross all voxels comprise the vector
\begin{equation}
  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
  + {\bf D}_c (\vect{\sigma} \odot {\bf n})
  \;\;.
  \label{eq:tautotal}
\end{equation}
This vector depends on the variables $\vect{\sigma}$ and ${\bf n}$
(See~\cref{fig:projection}a).

@@

Per camera $c$ and voxel $k$, the lines $[{\rm SR},k]$ and $[{\rm
  LOS}_c,k]$ intersect at a fixed angle $\Phi^{\rm scatter}_c(k)$,
which is pre-calculated.  Column-stacking all voxels yields the vector
representation of all scattering angles in the domain,
$\vect{\Phi}^{\rm scatter}_c$ per camera $c$. Similarly, the
single-scattering albdeos $\varpi^{\rm aerosol}$ in all voxels are
stacked to vector $\vect{\varpi}$.  Using
\cref{eq:alphabasic,eq:rayleighP,eq:betaer,eq:betair}, the angular
scattering coefficients across the domain are expressed in vector form
by
\begin{align}
  \tilde{\vect{\alpha}}^{\rm air}_c &=
  \vect{\beta}^{\rm air} \odot P^{\rm air}(\vect{\Phi}^{\rm scatter}_c) \nonumber \\
  \tilde{\vect{\alpha}}^{\rm aerosol}_c &= \vect{\varpi}\odot
  \vect{\sigma} \odot {\bf n} \odot P^{\rm aerosol}_{\bf
    g}(\vect{\Phi}^{\rm scatter}_c)
  \label{eq:alpha_matrix}
\end{align}
The vector ${\bf g}$ column-stacks the anisotropy parameter of the
phase function, in all voxels. We use this notation, to indicate a
parametric phase function as in \cref{eq:aerosol_scatter}.

@@

Compounding the attenuation of irradiance along both $[{\rm SR},k]$
and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
(\cref{eq:beer-lambert,eq:betair,eq:tautotal}) the radiant power
contributed by the voxel is
\begin{equation}
  p_c(k)= L^{\rm TOA}
  [\tilde{\alpha}^{\rm air}_c(k) + \tilde{\alpha}^{\rm aerosol}_c(k)]
  e^{-\tau_c(k)}
  \;\;,
  \label{eq:ick}
\end{equation}
where $L^{\rm TOA}$ is the radiance at the TOA. A column-stack vector
of all voxel contributions is
\begin{equation}
  {\bf p}_c= L^{\rm TOA}
  [\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm aerosol}_c]
  \odot e^{-\vect{\tau}_c}
  \;\;.
  \label{eq:pc}
\end{equation}

A camera pixel collects light from a narrow cone in the
atmosphere. The cone includes some voxels, intersects with some other
voxels, and oblivious to all the rest~(\cref{fig:projection}b).
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{0.8\columnwidth}\input{images/light_transfer.pdf_tex}}
  \caption{\small [a] Irradiance of voxel $k$ is attenuated by voxels
    above it on a SR. The scattered radiance from voxel $k$ is then
    attenuated by voxels below it on a LOS to camera $c$.  [b] An
    image pixel captures light emanating in a cone in space. Voxels
    that fully or partially fall in this cone are sensed by the
    pixel.}
  \label{fig:projection}
\end{figure}
Thus light power captured at a pixel is a weighted sum of the power
$p_c(k)$ from all voxels.  This linear sum is formulated by a matrix
operation over ${\bf p}_c$. The measured image is column-stacked to a
vector $N_{\rm pix}$ long. It is given by
\begin{equation}
  {\bf i}_c= {\vect{\Pi}}_c{\bf p}_c
  \;\;.
  \label{eq:IcP}
\end{equation}

Combining \cref{eq:tautotal,eq:pc,eq:IcP}, the captured image is thus
\begin{align}
  {\bf i}_c= L^{\rm TOA} {\vect{\Pi}}_c \left\{
    (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm
      aerosol}_c) \odot e^{-[\vect{\tau}_c^{\rm air} + {\bf D}_c
      (\vect{\sigma} \odot {\bf n})]} \right\}
  \label{eq:bigIc}
\end{align}

To simplify the case in study, let us assume there is only a single
type of aerosol over a scene. Hence, the three-element vector
$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
the scene, but the density distribution ${\bf n}$ is variable. Then,
\cref{eq:bigIc} degenerates to
\begin{align}
  {\bf i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{ e^{-(\vect{\tau}_c^{\rm
      air} + {\sigma}^{\rm aerosol} {\bf D}_c {\bf n}) }\odot
  [\tilde{\vect{\alpha}}^{\rm air}_c + 
  \varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
    aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bf n} ] \Big\} .
  \label{eq:bigIA}
\end{align}

@@

In general terms, the variables are the set
\begin{equation}
  {\cal V}\equiv
  \left\{
    {\bf n},
    \left\{
      \vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bf g}_{\lambda}
    \right\}_{\lambda}
  \right\}
  \;\;,
  \label{eq:calV}
\end{equation}
where $\lambda$ denotes the spectral (color) channel.  There are
$N_{\rm spectral}$ spectral channels.  Thus, the number of unknown
variables is in principle \mbox{$|{\cal V}|=N_{\rm voxels}(1+3N_{\rm
    spectral})$}.

Prior knowledge reduces the unknowns. For simplicity we assume a
single aerosol type dominates a scene. Furthermore, in the following
section we assume that we know the type of the particle. Hence, we
focus here on retrieving ${\bf n}$.

@@

The recovery task is phrased as optimization of an objective function,
that fits the image-formation model (\cref{eq:bigIc,eq:bigIA}) to
measured photographs $\{ {\bf i}^{\rm measured}_c\}_{c=1}^{N_{\rm
    views}}$:
\begin{equation}
  \label{eq:minobjectiveA}
  \hat{\bf n} =
  \argmin_{{\bf n}} F({\bf n})
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  F({\bf n})
  = \sum_{c=1}^{N_{\rm views}}
  \| {\bf i}^{\rm measured}_c - {\bf i}_c({\bf n})\|^2_2
\end{equation}
This is solved using standard optimization tools.  The gradient of $F$
with respect to ${\bf n}$ is
\begin{align}
  \Grad{{\bf n}} F = -2\sum_{c=1}^{N_{\rm views}}
  \transpose{\left[{\bf J}_{{\bf i}_c}({\bf n})\right]} [{\bf i}^{\rm
    measured}_c - {\bf i}_c({\bf n})] \;.
  \label{eq:gradient1}
\end{align}
Here the matrix ${\bf J}_{{\bf i}_c}({\bf n})$ is the Jacobian of the
vector ${\bf i}_c$ with respect to ${\bf n}$. A close-form expression
of our Jacobian is
\begin{align}
  {\bf J}_{{\bf i}_c}({\bf n}) &= L^{\rm TOA}({\bf A}-{\bf B}){\bf C}
  ,
  \label{eq:gradient2}
\end{align}
where
\begin{align}
  \label{eq:gradient3}
  {\bf A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
  {\bf B} &= {\sigma}^{\rm aerosol}\transpose{{\bf D}_c} \nonumber\\
  & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
      scatter}_c) \odot{\bf n}
    ]} \nonumber \\
  {\bf C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
      aerosol} {\bf D}_c {\bf n})]} \transpose{{\vect{\Pi}}_c}
\end{align}
For a detailed derivation of \cref{eq:gradient2,eq:gradient3}, we
refer the reader to \cref{sec:gradient-derivation}.

@@

The second function, $w_2$, expresses a clustered nature of aerosol
``clouds''. We define blobs in the form of 3D ellipsoids. There may be
multiple ellipsoids suspended.  Then
\begin{equation}
  w_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then
\begin{equation}
  \label{eq:ntrue}
  {\bf n}^{\rm true}={\bf w}_1\odot {\bf w}_2  .
  \hspace{-0.05cm}
\end{equation}
As an example, we created a {\em Haze Blobs} scene using two ellipsoid
blobs (\cref{fig:simulation1}a):
\begin{figure} \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/simulation1}}
  \caption{\small [a] Simulated 3D aerosol distribution composed of
    {\em Haze Blobs}. [b] Its reconstruction. Color represents aerosol
    density. The density units are $10^{15}~{\rm particles}/{\rm
      cm}^3.$}
  \label{fig:simulation1}
\end{figure}
the first is centered at altitude \SI{3.3}{\km}, and has horizontal
width of \SI{32}{\km} and vertical thickness of \SI{2.8}{\km}. The
second ellipsoid is centered at altitude \SI{6.6}{\km}, and has
lateral width of \SI{24}{\km} and vertical thickness of
\SI{2.1}{\km}. Note that the horizontal widths are much larger than
the vertical ones. This is consistent with scales of atmospheric
aerosol distributions.

@@

\noindent{\bf Optimization}: We used the L-BFGS-B
algorithm~\cite{BFGS}. The algorithm was initialized by ${\bf
  n}=0$. Satisfactory convergence occurred in several thousand
iterations, taking a couple of hours to complete in total.

@@

An iso-surface visualization of the original {\em Haze Blobs}
distribution is shown in \cref{fig:simulation1}a, while the recovered
3D distribution is visualized in \cref{fig:simulation1}b. The
distributions appear consistent, though there are errors that stem
from the random noise in the images. To quantify the results, we use a
relative error measure based on the $\ell_1$ norm
\begin{equation}
  \label{eq:ndiff}
  \epsilon=\frac{\| \hat{\bf n}  - {\bf n}^{\rm true} \|_1}
  {\| {\bf n}^{\rm true} \|_1} ,
  \hspace{-0.05cm}
\end{equation}
It is equivalent to the aerosol mass that is over and under-estimated
in all voxels, relative to the total aerosol mass in the scene.  In
the {\em Haze Blobs} case, $\epsilon=0.202$.

@@

>>>>

Consider \cref{fig:groundgrid}.  Ground-based wide-angle sky-cameras
capture the sky lightfield from below. Per viewpoint, the view azimuth
and elevation angles (relative to the zenith and north) are
encapsulated in the vector ${\bm{\Theta}}$.  A raw image is $i_{\bm
  x}({\bm{\Theta}})$: a camera's location ${\bm x}$ is fixed, while
any pixel in a frame represents an angle ${\bm{\Theta}}$.  The
measured radiance in all locations ${\bm x}$ and angles
${\bm{\Theta}}$ is the {\em lightfield} $I({\bm
  x},{\bm{\Theta}})$. Individual images are slices of the lightfield.

@@

The number of voxels is $N_{\rm voxels}$. All their associated
variables are concatenated into columns stack vectors, each $N_{\rm
  voxels}$ long. Aerosol densities and cross sections in all voxels
are stored in the respective vectors ${\bm n}$ and
$\vect{\sigma}$. Define a $N_{\rm voxels}\times N_{\rm voxels}$ sparse
matrix ${\bm D}^{\mathrm{Sun \rightarrow voxel}}$, whose element
$(k,q)$ is
\begin{equation}
  D^{\mathrm{Sun \rightarrow voxel}}(k,q) =
  \left\{
    \begin{array}{ll}
      l_{\rm SR}(q) & \mbox{ if $q \in[{\rm SR},k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dsv}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
\cref{eq:lSRaeros,eq:Dsv} lead to a vector of SR optical depths due to
aerosols (See \cref{fig:projection})a:
\begin{equation}
  \vect{\tau}_{\rm SR}^{\rm aerosol}=
  {\bm D}^{\mathrm{Sun \rightarrow voxel}}
  (\vect{\sigma} \odot {\bm n})
  \label{eq:tauSRvec1}
\end{equation}
where the operator $\odot$ denotes the Hadamard (element-wise)
product. Similarly, \cref{eq:lSRair} leads to a vector of SR optical
depths due to air, $\vect{\tau}_{\rm SR}^{\rm air}$.

Analogously, for camera $c$, denote by $[{\rm LOS}_c,k]$ a LOS bounded
between the camera and the center of voxel $k$. The LOS zenith angle
is $\Phi^{\rm LOS}_c$.  This LOS intersects voxel $q$. The geometric
length of this intersection line segment is $l_{\rm LOS_c}(q)$which
depends on $\Delta z$, $\Phi^{{\rm LOS}_c}$ and $q$.  Analogously to
\cref{eq:lSRaa,eq:lSRair,eq:lSRaeros}, the optical depth along a LOS
to $k$ is
\begin{equation}
  \tau_{{\rm LOS}_c}(k)=
  \tau_{{\rm LOS}_c}^{\rm air}(k) +  \tau_{{\rm LOS}_c}^{\rm aerosol}(k)
  \;\;,
  \label{eq:lLOSaerot}
\end{equation}
where
\begin{equation}
  \tau_{{\rm LOS}_c}^{\rm air}(k)=
  \sum_{q \in[{\rm LOS}_c,k]}
  \beta^{\rm air}(q)  l_{\rm LOS_c}(q)
  \label{eq:lLOSair}
\end{equation}
and
\begin{align}
  \label{eq:lLOSaeros}
  \tau_{{\rm LOS}_c}^{\rm aerosol}(k) = \sum_{q \in[{\rm LOS}_c,k]}
  \sigma^{\rm aerosol}(q) n^{\rm aerosol}(q) l_{\rm LOS_c}(q).
\end{align}
\cref{eq:lLOSaeros} leads to a vector of LOS optical depths due to
aerosols:
\begin{equation}
  \vect{\tau}_{{\rm LOS}_c}^{\rm aerosol}=
  {\bm D}^{\mathrm{voxel \rightarrow cam}}_c
  (\vect{\sigma} \odot {\bm n})
  \label{eq:tauLOSvec1}
\end{equation}
Here ${\bm D}^{\mathrm{voxel \rightarrow cam}}_c$ is a $N_{\rm
  voxels}\times N_{\rm voxels}$ sparse matrix whose element $(k,q)$ is
\begin{equation}
  D^{\mathrm{voxel \rightarrow cam}}_c(k,q) =
  \left\{
    \begin{array}{ll}
      l_{\rm LOS_c}(q) & \mbox{ if $q \in[{\rm LOS}_c,k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dvc}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
Similarly, \cref{eq:lSRair} leads to a vector of LOS optical depths
due to air, $\vect{\tau}_{{\rm LOS}_c}^{\rm air}$.

The fixed sparse matrices ${\bm D}^{\mathrm{Sun \rightarrow voxel}}$
and ${\bm D}^{\mathrm{voxel \rightarrow cam}}_c$ are compounded to a
single matrix
\begin{equation}
  {\bm D}_c=
  {\bm D}^{\mathrm{Sun \rightarrow voxel}}+
  {\bm D}^{\mathrm{voxel \rightarrow cam}}_c
  \;\;.
  \label{eq:Dtotal}
\end{equation}
Similarly, the molecular optical depths along all trajectories between
the sun, each voxel and camera $c$ are compounded to a vector
\begin{equation}
  \vect{\tau}_c^{\rm air}=
  \vect{\tau}_{\rm SR}^{\rm air}+
  \vect{\tau}_{{\rm LOS}_c}^{\rm air}
  \;\;.
  \label{eq:tauairtotal}
\end{equation}
Using \cref{eq:rayleighbeta} for $\beta^{\rm air}$ in all voxels, the
vector $\vect{\tau}_c^{\rm air}$ is fixed. Thus $\vect{\tau}_c^{\rm
  air}$ can be calculated once, per sun zenith angle.

Using
\cref{eq:lSRaa,eq:tauSRvec1,eq:lLOSair,eq:tauLOSvec1,eq:Dtotal,eq:tauairtotal},
the total optical depths corresponding to LOSs (of camera $c$) and SRs
that cross all voxels comprise the vector
\begin{equation}
  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
  + {\bm D}_c (\vect{\sigma} \odot {\bm n})
  \;\;.
  \label{eq:tautotal}
\end{equation}
This vector depends on the variables $\vect{\sigma}$ and ${\bm n}$
(See~\cref{fig:projection}a).

@@

Per camera $c$ and voxel $k$, the lines $[{\rm SR},k]$ and $[{\rm
  LOS}_c,k]$ intersect at a fixed angle $\Phi^{\rm scatter}_c(k)$,
which is pre-calculated.  Column-stacking all voxels yields the vector
representation of all scattering angles in the domain,
$\vect{\Phi}^{\rm scatter}_c$ per camera $c$. Similarly, the
single-scattering albdeos $\varpi^{\rm aerosol}$ in all voxels are
stacked to vector $\vect{\varpi}$.  Using
\cref{eq:alphabasic,eq:rayleighP,eq:betaer,eq:betair}, the angular
scattering coefficients across the domain are expressed in vector form
by
\begin{align}
  \tilde{\vect{\alpha}}^{\rm air}_c &=
  \vect{\beta}^{\rm air} \odot P^{\rm air}(\vect{\Phi}^{\rm scatter}_c) \nonumber \\
  \tilde{\vect{\alpha}}^{\rm aerosol}_c &= \vect{\varpi}\odot
  \vect{\sigma} \odot {\bm n} \odot P^{\rm aerosol}_{\bm
    g}(\vect{\Phi}^{\rm scatter}_c)
  \label{eq:alpha_matrix}
\end{align}
The vector ${\bm g}$ column-stacks the anisotropy parameter of the
phase function, in all voxels. We use this notation, to indicate a
parametric phase function as in \cref{eq:aerosol_scatter}.

@@

Compounding the attenuation of irradiance along both $[{\rm SR},k]$
and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
(\cref{eq:beer-lambert,eq:betair,eq:tautotal}) the radiant power
contributed by the voxel is
\begin{equation}
  p_c(k)= L^{\rm TOA}
  [\tilde{\alpha}^{\rm air}_c(k) + \tilde{\alpha}^{\rm aerosol}_c(k)]
  e^{-\tau_c(k)}
  \;\;,
  \label{eq:ick}
\end{equation}
where $L^{\rm TOA}$ is the radiance at the TOA. A column-stack vector
of all voxel contributions is
\begin{equation}
  {\bm p}_c= L^{\rm TOA}
  [\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm aerosol}_c]
  \odot e^{-\vect{\tau}_c}
  \;\;.
  \label{eq:pc}
\end{equation}

A camera pixel collects light from a narrow cone in the
atmosphere. The cone includes some voxels, intersects with some other
voxels, and oblivious to all the rest~(\cref{fig:projection}b).
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{0.8\columnwidth}\input{images/light_transfer.pdf_tex}}
  \caption{\small [a] Irradiance of voxel $k$ is attenuated by voxels
    above it on a SR. The scattered radiance from voxel $k$ is then
    attenuated by voxels below it on a LOS to camera $c$.  [b] An
    image pixel captures light emanating in a cone in space. Voxels
    that fully or partially fall in this cone are sensed by the
    pixel.}
  \label{fig:projection}
\end{figure}
Thus light power captured at a pixel is a weighted sum of the power
$p_c(k)$ from all voxels.  This linear sum is formulated by a matrix
operation over ${\bm p}_c$. The measured image is column-stacked to a
vector $N_{\rm pix}$ long. It is given by
\begin{equation}
  {\bm i}_c= {\vect{\Pi}}_c{\bm p}_c
  \;\;.
  \label{eq:IcP}
\end{equation}

Combining \cref{eq:tautotal,eq:pc,eq:IcP}, the captured image is thus
\begin{align}
  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \left\{
    (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm
      aerosol}_c) \odot e^{-[\vect{\tau}_c^{\rm air} + {\bm D}_c
      (\vect{\sigma} \odot {\bm n})]} \right\}
  \label{eq:bigIc}
\end{align}

To simplify the case in study, let us assume there is only a single
type of aerosol over a scene. Hence, the three-element vector
$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
the scene, but the density distribution ${\bm n}$ is variable. Then,
\cref{eq:bigIc} degenerates to
\begin{align}
  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{ e^{-(\vect{\tau}_c^{\rm
      air} + {\sigma}^{\rm aerosol} {\bm D}_c {\bm n}) }\odot
  [\tilde{\vect{\alpha}}^{\rm air}_c + 
  \varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
    aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm n} ] \Big\} .
  \label{eq:bigIA}
\end{align}

@@

In general terms, the variables are the set
\begin{equation}
  {\cal V}\equiv
  \left\{
    {\bm n},
    \left\{
      \vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm g}_{\lambda}
    \right\}_{\lambda}
  \right\}
  \;\;,
  \label{eq:calV}
\end{equation}
where $\lambda$ denotes the spectral (color) channel.  There are
$N_{\rm spectral}$ spectral channels.  Thus, the number of unknown
variables is in principle \mbox{$|{\cal V}|=N_{\rm voxels}(1+3N_{\rm
    spectral})$}.

Prior knowledge reduces the unknowns. For simplicity we assume a
single aerosol type dominates a scene. Furthermore, in the following
section we assume that we know the type of the particle. Hence, we
focus here on retrieving ${\bm n}$.

@@

The recovery task is phrased as optimization of an objective function,
that fits the image-formation model (\cref{eq:bigIc,eq:bigIA}) to
measured photographs $\{ {\bm i}^{\rm measured}_c\}_{c=1}^{N_{\rm
    views}}$:
\begin{equation}
  \label{eq:minobjectiveA}
  \hat{\bm n} =
  \argmin_{{\bm n}} F({\bm n})
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  F({\bm n})
  = \sum_{c=1}^{N_{\rm views}}
  \| {\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})\|^2_2
\end{equation}
This is solved using standard optimization tools.  The gradient of $F$
with respect to ${\bm n}$ is
\begin{align}
  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
    measured}_c - {\bm i}_c({\bm n})] \;.
  \label{eq:gradient1}
\end{align}
Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
vector ${\bm i}_c$ with respect to ${\bm n}$. A close-form expression
of our Jacobian is
\begin{align}
  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}({\bm A}-{\bm B}){\bm C}
  ,
  \label{eq:gradient2}
\end{align}
where
\begin{align}
  \label{eq:gradient3}
  {\bm A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
  {\bm B} &= {\sigma}^{\rm aerosol}\transpose{{\bm D}_c} \nonumber\\
  & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
      scatter}_c) \odot{\bm n}
    ]} \nonumber \\
  {\bm C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
\end{align}
For a detailed derivation of \cref{eq:gradient2,eq:gradient3}, we
refer the reader to \cref{sec:gradient-derivation}.

@@

The second function, $w_2$, expresses a clustered nature of aerosol
``clouds''. We define blobs in the form of 3D ellipsoids. There may be
multiple ellipsoids suspended.  Then
\begin{equation}
  w_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then
\begin{equation}
  \label{eq:ntrue}
  {\bm n}^{\rm true}={\bm w}_1\odot {\bm w}_2  .
  \hspace{-0.05cm}
\end{equation}
As an example, we created a {\em Haze Blobs} scene using two ellipsoid
blobs (\cref{fig:simulation1}a):
\begin{figure} \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/simulation1}}
  \caption{\small [a] Simulated 3D aerosol distribution composed of
    {\em Haze Blobs}. [b] Its reconstruction. Color represents aerosol
    density. The density units are $10^{15}~{\rm particles}/{\rm
      cm}^3.$}
  \label{fig:simulation1}
\end{figure}
the first is centered at altitude \SI{3.3}{\km}, and has horizontal
width of \SI{32}{\km} and vertical thickness of \SI{2.8}{\km}. The
second ellipsoid is centered at altitude \SI{6.6}{\km}, and has
lateral width of \SI{24}{\km} and vertical thickness of
\SI{2.1}{\km}. Note that the horizontal widths are much larger than
the vertical ones. This is consistent with scales of atmospheric
aerosol distributions.

@@

\noindent{\bf Optimization}: We used the L-BFGS-B
algorithm~\cite{BFGS}. The algorithm was initialized by ${\bm
  n}=0$. Satisfactory convergence occurred in several thousand
iterations, taking a couple of hours to complete in total.

@@

An iso-surface visualization of the original {\em Haze Blobs}
distribution is shown in \cref{fig:simulation1}a, while the recovered
3D distribution is visualized in \cref{fig:simulation1}b. The
distributions appear consistent, though there are errors that stem
from the random noise in the images. To quantify the results, we use a
relative error measure based on the $\ell_1$ norm
\begin{equation}
  \label{eq:ndiff}
  \epsilon=\frac{\| \hat{\bm n}  - {\bm n}^{\rm true} \|_1}
  {\| {\bm n}^{\rm true} \|_1} ,
  \hspace{-0.05cm}
\end{equation}
It is equivalent to the aerosol mass that is over and under-estimated
in all voxels, relative to the total aerosol mass in the scene.  In
the {\em Haze Blobs} case, $\epsilon=0.202$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%  Appendix  %%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
